\vspace{1.0cm} \Large \bf Supplemental material of ``Health and disease imprinted in the time variability of the human microbiome''

### 2016-09-23 mSystems/mSys_MAIN.tex
mSystems: docs of the initial submission
On branch master
	new file:   CoverLetter.DOC
	new file:   CoverLetter.pdf
	deleted:    MSWord_OBSOLETE/WHOLE_draft_0.1.docx
	deleted:    MSWord_OBSOLETE/discussion_draft_0.1.docx
	deleted:    MSWord_OBSOLETE/intro_draft_0.1.docx
	deleted:    MSWord_OBSOLETE/intro_draft_0.2.docx
	deleted:    MSWord_OBSOLETE/mat_met_draft_0.3.docx
	deleted:    MSWord_OBSOLETE/results_draft_0.1.docx
	deleted:    MSWord_OBSOLETE/skeleton_draft_0.3.docx
	new file:   mSys_MAIN.docx
	modified:   mSys_MAIN.pdf
	modified:   mSys_MAIN.tex
	modified:   mSys_suppl.pdf
	modified:

% release codenumber (update it here!)
\newcommand\releasecode{$\beta$}

@@

% watermarks (time consuming!)
\newwatermark[allpages,color=Green!4,angle=45,scale=12,xpos=-60,ypos=0]{RC\releasecode}
\newwatermark[allpages,color=Green!12,angle=0,scale=1,xpos=0,ypos=137]{
\emph{mSystems} \LaTeX\ manuscript RC\releasecode}

>>>>

% release codenumber (update it here!)
\newcommand\releasecode{initial}

@@

% watermarks (time consuming!)
\newwatermark[allpages,color=Purple!4,angle=45,scale=7,xpos=-40,ypos=0]{submitted}
\newwatermark[allpages,color=Purple!12,angle=0,scale=1,xpos=0,ypos=137]{
\emph{mSystems} \LaTeX\ manuscript \releasecode\ submission}
